---
title: "Homework 2"
author: "Montgomery Inman"
date: "2/2/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Due: 2/9/2022 before 11:59pm. Submit in Canvas (file upload).

1. Finish the in-class practice in Slides 3-12 in "Lecture 2-2-Practice for git", link: https://yumouqiu.github.io/DS202-Spring2022/Practice/practice01.html  
    a. Download the RMarkdown file with these homework instructions to use as a template for your work. Make sure to replace "Your Name" with your name.  
    b. In the RMarkdown file, write down table of team members, and their github repository links;   
the number of successful pull requests you made, and the github repository to which you requested a change;  
the number of pull requests you accepted, and the github repository from which you accepted.  
    c. Write down a list with at least 3 tips of how to make working with git/github easier  
    
    
##B) 

```{r}
members = c('Montgomery Inman','INSERT NAME')
link = c('https://github.com/montgomeryinman/HW2.git', 'INSERT LINK')
num_pull = c('INSERT NUMBER', 'INSERT NUMBER')
link_req = c('INSERT LINK','https://github.com/montgomeryinman/HW2.git')

question_b = data.frame(members, link, num_pull, link_req)
knitr :: kable(question_b, 'pipe', col.names = c('Members', 'Link', 'Number of pull requests','Link Requested From'), align = c('c','c','c','c'))
```
##C) 
1. Look at Youtube videos/tutorials
2. Ask questions
3. Google questions 

2. Generate the graph of LifExp vs. gdpPercap for US, Canada (fixed data) and Australia by RMarkdown based on the data set "gapminder-5060", like what we did in the class.  
Please use Github to collaborate on this problem. For example, one member can create the plot of US in his/her repository. The other member will fork this repository, add the result for the second country, and make a pull request for merging into the main repository. Each member should at least analyze one country and make at least one pull request. **Please submit the RMarkdown file, the output file, and the screen shot of the successful pull request and the merge.**


```{r}
library(tidyverse)
library(dplyr)
#Filtering just the US data 
    US <- df %>% 
      filter(country =='United States')
# Reading in file
df = read.csv('/Users/montgomeryinman/Desktop/gapminder-5060.csv')

#Plotting the United States data
ggplot(US, aes(x = lifeExp, y = gdpPercap)) + geom_point()

```
```{r}

library(dplyr)
#Filtering to just Canada data frame
Canada <- df %>% 
      filter(country =='Canada')

#Changing the wrong value in Canada lifeExp
Canada_new <- Canada %>% mutate(lifeExp = replace(lifeExp, lifeExp == 999999.00, 69.96))

#Plotting the Canada graph
ggplot(Canada_new, aes(x = lifeExp, y = gdpPercap)) + geom_point()
```





### NEED TO DO AUSTRALIA ###





3. Write a paragraph (~200 words) describing an example of what you consider data science. Write your paragraph in R Markdown. Include at least 
    a. one link to a chart or an image and 
    b. at least one itemized or enumerated list.
--------------------------------------------------------------------------------------------------------
3) I consider data science to be a field in where data is examined and used to make better, more efficient decisions. A specific example of data science that I am interested in is how data science is implemented in the NBA, MLB, NFL, and other sports. In the MLB, countless data points are collected from how many times the ball spins to how many homeruns a player has hit. Data science is used in the NBA in numerous ways; game strategy, which player to draft, who to sign in free agency, and many other ways. A basic example includes a player's shot chart.

-(https://www.nba.com/stats/events/?flag=3&CFID=33&CFPARAMS=2021-22&PlayerID=201942&TeamID=0&GameID=&ContextMeasure=FGA&Season=2021-22&SeasonType=Regular%20Season&LeagueID=00&PerMode=PerGame&Split=general&PlusMinus=N&PaceAdjust=N&Rank=N&Outcome=&Location=&Month=0&SeasonSegment=&OpponentTeamID=0&VsConference=&VsDivision=&GameSegment=&Period=0&LastNGames=0&DateFrom=&DateTo=&PORound=0&ShotClockRange=&MeasureType=Base&section=player&sct=hex) - 

or a list of a players stats and how efficient they are from certain areas of the basketball court.

-(https://www.nba.com/stats/player/201942/shooting/)

In these examples of DeMar Derozan's shot chart and shooting splits from location, we can see he is very efficient from the midrange, but pretty bad from 3 point range.The process of collecting the data points and then creating a visual chart to communicate those results is essentially what Data Science is to me.
    
--------------------------------------------------------------------------------------------------------

Note: your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. Including the link to the image is the tricky part here. Make sure that you don't use any file structure that depends on your computing environment.


For the submission: submit your solution in an **R Markdown file** and (just for insurance) submit the corresponding html (or Word) file with it. 
